|

### 2021-10-15 manuscript/manuscript.Rmd
GSPA poster+abstract: incorporated feedback B, massive overhaul.

@@

@@

p2 <- raincloud_2x3_repmes(
  data = df_2x3,
  colors = colors,
  fills = colors,
  size = 1,
  alpha = .7,
  ort = "h") + #set to v for vertical plot

@@

  annotate(geom = "text", 
           label = "Single-analyst", 
           x = 3.8, y = 13, size = 6,
           family = "serif") + 
  annotate(geom = "text", 
           label = "Multi-consistent", 
           x = 2.73, y = 14, size = 6,
           family = "serif") + 
  annotate(geom = "text", 
           label = "Multi-inconsistent",
           x = 1.78, y = 16, size = 6,
           family = "serif") + 
  annotate(geom = "text", 
           label = "Prior Beliefs", 
           fontface = "bold",
           x = 4.2, y = 26, size = 8, 
           color = "#035AA6",
           family = "serif") + 
  annotate(geom = "text", 
           label = "vs.", 
           x = 4.2, y = 45, size = 8,
           family = "serif") + 
  annotate(geom = "text", 
           label = "Posterior Beliefs", 
           fontface = "bold",
           x = 4.2, y = 68, size = 8, 
           color = "darkorange",
           family = "serif") +

  theme_classic() +
  theme(axis.ticks.y = element_blank(),
        #axis.text = element_text(size = 9),
        axis.title.y = element_blank(),
        text = element_text(size = 16, family = "serif"))

@@

>>>>

get_d <- function(Predictor, Multi_Condition = "Consistent") {
  linear_mod <- lm(
    pull(df, {{ Predictor }}) ~ Condition + Prior_beliefs, data = df)

  ifelse(Multi_Condition == "Consistent",
         parse_number(apa_results$table$statistic[2])/sqrt(499),
         parse_number(apa_results$table$statistic[3])/sqrt(500)) 
}

@@

cohens_d <- parse_number(gsub(".*=", "", t_test$statistic)) / sqrt(499)

t_apa <- paste(t_test$estimate, 
               strsplit(t_test$statistic, ",")[[1]][2], #take out t-value
               sep = ", ")

# Post-hoc t-test
df_multi_inconsistent <- df %>% 
  filter(Condition == "Multi-inconsistent")

t_test <- apa_print(t.test(df_multi_inconsistent$Final_beliefs,
                           df_multi_inconsistent$Prior_beliefs, 
                           paired = TRUE))

t_apa <- paste(t_test$estimate, 
               strsplit(t_test$statistic, ",")[[1]][2], #take out t-value
               sep = ", ")

# Post-hoc t-test
df_single <- df %>% 
  filter(Condition == "Single")

t_test <- apa_print(t.test(df_single$Final_beliefs,
                           df_single$Prior_beliefs, 
                           paired = TRUE))

@@

raincloud <- function(label_c1, label_c2, label_c3){
  raincloud_2x3_repmes(
  data = df_2x3,
  colors = colors,
  fills = colors,
  size = 1,
  alpha = .7,
  ort = "h") + #set to v for vertical plot

@@

  annotate(geom = "text", 
           label = label_c1, 
           x = 3.8, y = 13, size = 6,
           family = "serif") + 
  annotate(geom = "text", 
           label = label_c2, 
           x = 2.73, y = 14, size = 6,
           family = "serif") + 
  annotate(geom = "text", 
           label = label_c3,
           x = 1.78, y = 16, size = 6,
           family = "serif") + 
  annotate(geom = "text", 
           label = "Prior Beliefs", 
           fontface = "bold",
           x = 4.2, y = 26, size = 8, 
           color = "#035AA6",
           family = "serif") + 
  annotate(geom = "text", 
           label = "vs.", 
           x = 4.2, y = 45, size = 8,
           family = "serif") + 
  annotate(geom = "text", 
           label = "Posterior Beliefs", 
           fontface = "bold",
           x = 4.2, y = 68, size = 8, 
           color = "darkorange",
           family = "serif") +

  theme_classic() +
  theme(axis.ticks.y = element_blank(),
        #axis.text = element_text(size = 9),
        axis.title.y = element_blank(),
        text = element_text(size = 16, family = "serif"))
}

p2 <- raincloud("Single-analyst", "Multi-consistent", "Multi-inconsistent")

@@

p3 <- raincloud("Single estimate", "Consistent crowd", "Inconsistent crowd")

ggsave(here("poster/Figure2b.jpg"), p3, 
       width = 7, height = 5, units = "in") #save to poster folder

### 2021-10-15 poster/GSPA_Abstract.Rmd
GSPA poster+abstract: incorporated feedback B, massive overhaul.

---
title: |
  | Lay Perceptions of Scientific Findings:
  | The Risks of Variability and Lack of Consensus
output: pdf_document
---

@@

Word count: 699

# Introduction

Crowd science is on the rise in behavioral science and aims to increase its credibility. Whether it does, however, remains untested: does crowd science improve lay perceptions of scientific findings?  
 $~~~~~~~$ We focus on crowdsourced data analysis: independent analysts estimate a parameter from the same dataset. We compare the effects of providing lay consumers with a single parameter estimate vs. multiple consistent (inconsistent) parameter estimates that show low (high) variance and high (low) consensus.  
 $~~~~~~~$ Table 1 reports our preregistered hypotheses: when laypeople observe multiple consistent (inconsistent) estimates from independent scientists, we expect -- compared to one estimate from a single team -- an increase (decrease) in posterior beliefs and credibility of the results, and a decrease (increase) in ratings of bias and error. In addition, we expect that the act of providing multiple estimates decreases confidence in the aggregate parameter estimate in both multi-estimate conditions.

@@

After participants report their prior beliefs about a research question ("Do religious people report higher well-being?"), we randomly allocate them to one of three conditions. In the single-analyst condition, a single team of six researchers reports a 5% increase in well-being among religious people; in the multi-consistent condition, six independent researchers report six low variance, high consensus estimates (2%, 4%, 5%, 5%, 6%, 8%; $M = 5\%, \sigma = 2\%$); in the multi-inconsistent condition, six independent researchers report six high variance, low consensus estimates (-6%, -2%, 5%, 5%, 12%, 16%; $M = 5\%, \sigma = 8.25\%$).  
 $~~~~~~~$ Afterwards, participants rate -- on a slider from 0% to 100% -- their posterior beliefs, the credibility of the results, their confidence in the aggregate 5% estimate, and the likelihood of researcher bias, error, and discretion.

@@

We sampled 1,498 participants from Prolific (native English speakers from the US and UK, over 18 years old). As preregistered, we regressed all outcomes on prior beliefs and condition (with the single-analyst condition as the reference category). Figure 1 displays the main findings. The multi-inconsistent condition decreased posterior beliefs, ratings of credibility, and confidence in the parameter estimate (standardized effect size *b* = -22.80, -6.54, and -9.09, respectively, all *p*s < .001), and increased ratings of bias, error, and discretion  (*b* = 6.68, 5.89, and 9.22, respectively, all *p*s < .001). The multi-consistent condition decreased posterior beliefs (*b* = -5.71, *p* < .001) and increased ratings of error (*b* = 3.59, *p* = .016) and discretion (*b* = 5.14, *p* < .001); we found no significant effects on ratings of credibility (*b* = 1.24, *p* = .380), confidence in the parameter estimate (*b* = 0.49, *p* = .749), or ratings of bias (*b* = 2.13, *p* = .192).     
 $~~~~~~~~$ As hypothesized, consuming multiple, inconsistent estimates decreases lay posterior beliefs, credibility of the results, confidence in the average parameter estimate, and increases ratings of bias and error. Unexpectedly, consuming multiple, consistent estimates lowers lay posterior beliefs and increases ratings of error. Although the multi-consistent condition performs worse or no better than the single-analyst condition for all outcomes, there is a significant, positive *absolute* effect on posterior beliefs within the multi-consistent condition ($M_d$ = 4.75, *p* < .001; see Figure 2). This finding clarifies that multi-analyst studies with consistent outcomes can potentially be convincing in their own right -- however, relative to conventional, single-analyst research, crowdsourced data analysis does not seem to improve lay perceptions of scientific findings.

@@

From the proliferation of big team science and large-scale replication initiatives to preregistration and registered reports, several scientific fields have undergone significant reform with the well-intended goal of improving the reliability of scientific research. However, as with any real-world intervention, scientific reform can impose high costs, lack effectiveness, or have unintended consequences.  
 $~~~~~~~~$ While partly instituted with the goal of improving the credibility of scientific research, lay consumers appear to resist the inherent variability and lack of consensus that often reflect the reality of multi-analyst research. To our surprise, even when results generated by independent analysts are largely consistent, lay consumers are less likely to believe in the reported phenomenon and more likely to think that the findings stem from error or idiosyncratic choices. Given the resource-intensity of crowdsourced data analysis (Silberzahn & Uhlmann, 2015), our findings suggest that scientists who hope to improve lay perceptions of scientific findings may need to think twice before implementing multi-analyst studies.

>>>>

---
title: "Lay Perceptions of Scientific Findings: Swayed by the Crowd?"
shorttitle        : "Lay Perceptions of Scientific Findings"

author:
  - name          : "First author name here"
    affiliation   : "1"
    corresponding : no    # Define only one corresponding author
    address       : ""
    email         : ""
  - name          : "Second author name here"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Insert affiliation here"

abstract: |

keywords          : "Crowd science, Many analysts, Multi-analyst, Variability, Research credibility"
wordcount         : "700"

bibliography      : ["references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_word
---

@@

Crowd science is on the rise in behavioral science and aims to increase its credibility. Whether it does, however, remains untested: does crowd science improve lay perceptions of scientific findings? We draw from theories on social norms and numerical cognition to hypothesize that consistent (inconsistent) crowd estimates will lead to higher (lower) posterior beliefs and credibility of the results, lower confidence in the precise average parameter estimate, and lower (higher) ratings of bias and error, than a single estimate.

@@

After participants report their prior beliefs about a research question ("Do religious people report higher well-being?"), we randomly allocate them to one of three conditions. In the single estimate condition, a single team of six researchers reports a 5% increase in well-being among religious people; in the consistent crowd condition, six independent researchers report six low variance, high consensus estimates (2%, 4%, 5%, 5%, 6%, 8%; $M = 5\%, \sigma = 2\%$); in the inconsistent crowd condition, six independent researchers report six high variance, low consensus estimates (-6%, -2%, 5%, 5%, 12%, 16%; $M = 5\%, \sigma = 8.25\%$).   
Afterwards, participants rate -- on a slider from 0% to 100% -- their posterior beliefs, the credibility of the results, their confidence in the aggregate 5% estimate, and the likelihood of researcher bias, error, and discretion.

@@

We sampled 1,498 participants from Prolific (native English speakers from the US and UK, over 18 years old). As preregistered, we regressed all outcomes on prior beliefs and condition (with the single estimate condition as the reference category). Compared to the single estimate condition, inconsistent crowd estimates decreased posterior beliefs (*b* = -22.80, *p* < .001, Cohen's *d* = -0.72), ratings of credibility (*b* = -6.54, *p* < .001, *d* = -0.21), and confidence in the parameter estimate (*b* = -9.09, *p* < .001, *d* = -0.26), and increased ratings of bias (*b* = 6.68, *p* < .001, *d* = 0.18), error (*b* = 5.89, *p* < .001, *d* = 0.18), and discretion (*b* = 9.22, *p* < .001, *d* = 0.29). Compared to the single estimate condition, consistent crowd estimates decreased posterior beliefs (*b* = -5.71, *p* < .001, *d* = -0.18) and increased ratings of error (*b* = 3.59, *p* = .016, *d* = 0.11) and discretion (*b* = 5.14, *p* < .001, *d* = 0.16); we found no significant effects on ratings of credibility (*b* = 1.24, *p* = .380, *d* = 0.04), confidence in the average parameter estimate (*b* = 0.49, *p* = .749, *d* = 0.01), or ratings of bias (*b* = 2.13, *p* = .192, *d* = 0.06).     
As hypothesized, inconsistent crowd estimates lead to lower posterior beliefs, credibility of the results, and confidence in the average parameter estimate, and higher ratings of bias and error, than a single estimate. Unexpectedly, consistent crowd estimates lead to lower posterior beliefs and higher ratings of error than a single estimate. On all outcomes, consuming consistent crowd estimates performs worse or no better than consuming a single estimate. However, it is worth noting that there is a positive difference between prior and posterior beliefs within the consistent crowd condition ($M_d$ = 4.75, *d* = 0.19, *p* < .001; see Figure 2). This finding clarifies that a consistent crowd may sway observers --- however, relative to the conventional reporting of non-crowdsourced estimates, crowd estimates do not seem to improve lay perceptions of scientific findings.

@@

From the proliferation of big team science and large-scale replication initiatives to preregistration and registered reports, several scientific fields have undergone significant reform with the well-intended goal of improving the reliability of scientific research. However, as with any real-world intervention, scientific reform can have unintended consequences.   
While partly instituted with the goal of improving the credibility of scientific research, lay consumers appear to resist the inherent variability and lack of consensus that often reflect the reality of crowd science. To our surprise, even when the results generated by an independent crowd are largely consistent and lead to the same qualitative conclusion, lay consumers seem to respond negatively to observing multiple, variable estimates. In the future, it is important for crowd scientists to consider how -- e.g., by drawing from research on science communication -- to effectively communicate variable estimates while preserving or perhaps even improving the credibility of scientific research.

### 2021-10-15 poster/GSPA_Poster.Rmd
GSPA poster+abstract: incorporated feedback B, massive overhaul.

---
title: |
  | Lay Perceptions of Scientific Findings:
  | The Risks of Variability and Lack of Consensus
author:
  - name: Insert first author name here 
    affil: 1
    orcid: ''
  - name: Insert second author name here
    affil: 1
affiliation:
  - num: 1
    address: Insert affiliation here
column_numbers: 3
#logoright_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
#logoleft_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
output: 
  posterdown::posterdown_html:
    self_contained: true
    css: style.css
knit: pagedown::chrome_print
font_family: 'Cabin'
titletext_fontfamily: 'Cabin'
primary_colour: "#035AA6"
accent_colour: "#035AA6"
sectitle2_textcol: "#035AA6"
---

@@

The **credibility of scientific research** is in doubt, among lay consumer (Hornsey & Fielding, 2017) and scientist (Pashler & Wagenmakers, 2021) alike. Several tools have been proposed to combat this "crisis of confidence" (Ibid., p. 528). One such tool is the **crowd science** approach: "the organization of scientific research in open and collaborative projects" (Franzoni & Sauermann, 2014, p. 1). We focus on **crowdsourced data analysis**, also known as the **many analysts** or **multi-analyst** approach: a crowd of scientists independently analyzes the same dataset to answer the same research question or estimate and report a parameter of interest.  
 $~~~~~$ According to science reformers, crowd-scientific findings that tell a consistent story should garner more confidence in the conclusions and **increase public faith in science** (Silberzahn et al., 2018; Uhlmann et al., 2019). Here, we ask if we can find empirical evidence for these claims: **Does crowdsourcing data analysis improve lay perceptions of scientific findings?**

**Objectives**

We explore **the effects of scientific findings emerging from a crowd of researchers** (vs. a typical research collaboration) **on lay consumers**' posterior beliefs, perceptions of credibility, confidence in an aggregate effect size estimate, and ratings of researcher bias, error, and discretion.  
 $~~~~~$ We compare the effects of providing lay consumers with a single parameter estimate (the **single-analyst** condition) vs. multiple parameter estimates that (a) vary slightly and are all positive, leading to the same qualitative conclusion (the **multi-consistent** condition) or (b) vary widely and are of both signs, leading to differing qualitative conclusions (the **multi-inconsistent** condition). In all three conditions, we emphasize that the given estimates average to 5%.

**Preregistered Hypotheses**

**Table 1**: *Predicted direction of effects*

| Measure | Multi-consistent | Multi-inconsistent |
| ------------- |  ------------- | ------------- | 
| 1. Posterior beliefs | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`  | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` |
|2. Credibility of the results | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` |
| 3. Confidence in the precise estimate  | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`  | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | 
| 4. Researcher bias | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` |
| 5. Researcher error | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` |
| 6. Researcher discretion | $~~~$ No prediction | $~~~$ No prediction |
*Note*. Table 1 indicates the predicted direction of effects for all outcomes, **compared to the single-analyst condition** and **controlling for prior beliefs** (a green plus/red minus indicates a positive/negative prediction, respectively). For example, we hypothesized that, compared to a single-analyst study and controlling for prior beliefs, ratings of credibility would be greater in the multi-consistent condition and lower in the multi-inconsistent condition.

@@

We run an experiment (*N* = 1,498) with **three conditions**  
`r icon_style(icons::fontawesome("dice-one"), scale = 1.5, fill = "#035AA6")` $~$ **Single-analyst**  
A single parameter estimate  
`r icon_style(icons::fontawesome("dice-two"), scale = 1.5, fill = "#035AA6")` $~$ **Multi-consistent**  
Multiple crowd estimates with low variance and high consensus  
`r icon_style(icons::fontawesome("dice-three"), scale = 1.5, fill = "#035AA6")` $~$ **Multi-inconsistent**  
Multiple crowd estimates with high variance and low consensus

@@

**Figure 1**: *Estimates relative to the single-analyst condition*
```{r, echo = FALSE, out.width='95%', fig.retina=3, fig.align='left'}
knitr::include_graphics("Figure1.jpg")
```
**In line with our hypotheses**, lay consumers of multi-analyst studies with **inconsistent** results  
`r icon_style(icons::fontawesome("arrow-circle-down"), scale = 1.5, fill = "red")` $~~~$ Have lower posterior beliefs  
`r icon_style(icons::fontawesome("arrow-circle-down"), scale = 1.5, fill = "red")` $~~~$ Find the results less credible  
`r icon_style(icons::fontawesome("arrow-circle-down"), scale = 1.5, fill = "red")` $~~~$ Have less confidence in the average effect size estimate  
`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~~$ Believe the results are more likely to stem from bias  
`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~~$ Believe the results are more likely to stem from error

**Contrary to our hypotheses**, lay consumers of multi-analyst studies with **consistent** results  
`r icon_style(icons::fontawesome("arrow-circle-down"), scale = 1.5, fill = "red")` $~~~$ Have lower posterior beliefs  
`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~~$ Believe the results are more likely to stem from error

We found **no significant effects** on  
`r icon_style(icons::fontawesome("question-circle"), scale = 1.5, fill = "grey")` $~~~$ Credibility of the results  
`r icon_style(icons::fontawesome("question-circle"), scale = 1.5, fill = "grey")` $~~~$ Confidence in the effect size estimate  
`r icon_style(icons::fontawesome("question-circle"), scale = 1.5, fill = "grey")` $~~~$ Ratings of bias

@@

For the additional **exploratory measure**, lay consumers of multi-analyst studies (both with **consistent** and **inconsistent** results)  
`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~~$ Perceive greater researcher degrees of freedom

**Figure 2**: *Distribution of prior and posterior beliefs by condition*  
```{r, echo = FALSE, out.width='90%', fig.retina=3, fig.align='center'}
knitr::include_graphics("Figure2.jpg")
```

# Discussion  
**Conclusion**  
`r icon_style(icons::fontawesome("sitemap"), scale = 1.3, fill = "#035AA6")` $~$ Crowdsourced data analysis has **many worthy uses**, but...    
`r icon_style(icons::fontawesome("hand-holding-usd"), scale = 1.3, fill = "#035AA6")` $~~$ It's highly **resource-intensive**    
`r icon_style(icons::fontawesome("exclamation-triangle"), scale = 1.3, fill = "#035AA6")` $~$ **Variability** and  **lack of consensus** may evoke negative responses
`r icon_style(icons::fontawesome("question-circle"), scale = 1.3, fill = "#035AA6")` $~~$ Surprisingly, even **multiple, consistent estimates may backfire**

**Future Directions**  
`r icon_style(icons::fontawesome("flask"), scale = 1.3, fill = "#035AA6")` $~~~$ Perceptions of **scientists**?  
`r icon_style(icons::fontawesome("comments"), scale = 1.3, fill = "#035AA6")` $~~$ **Science communication** and **communicating uncertainty**

**Open Science Statement**  
The preregistration, survey materials, data, and code that support the findings of this study are openly available on GitHub and the OSF.  
`r icon_style(icons::fontawesome("github"), scale = 1.3, fill = "#035AA6")` $~~$ [Insert GitHub link here]   
`r icon_style(icons::academicons("osf"), scale = 1.3, fill = "#035AA6")` $~~$ [Insert OSF link here]

>>>>

---
title: |
  | Lay Perceptions of Scientific Findings:
  | Swayed by the Crowd?
author:
  - name: Insert first author name here 
    affil: 1
    orcid: ''
  - name: Insert second author name here
    affil: 1
affiliation:
  - num: 1
    address: Insert affiliation here
column_numbers: 3
#logoright_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
#logoleft_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
output: 
  posterdown::posterdown_html:
    self_contained: true
    css: style.css
knit: pagedown::chrome_print
font_family: 'Cabin'
titletext_fontfamily: 'Cabin'
primary_colour: "#035AA6"
accent_colour: "#035AA6"
sectitle2_textcol: "#035AA6"
---

@@

Every day, important scientific findings are rejected at large. From man-made climate change to the safety and efficacy of Covid-19 vaccinations, **science skepticism** has run rampant among lay consumers in modern society (Hornsey & Fielding, 2017). To **increase public faith in science**, some have proposed the use of **crowd science** (Silberzahn et al., 2018; Uhlmann et al., 2019).  
 $~~~~~$ We explore whether high consensus and low variance in parameter estimates among a **crowd** (the **consistent crowd** condition) can improve **lay perceptions of scientific findings**. In line with **social norm theory** (Miller & Prentice, 2016), we expect that **observing consensus among a crowd** will -- compared to the conclusion of a single scientist (the **single estimate** condition) -- increase conformity in opinion. Drawing from work on **intuitive statistics** (Gigerenzer & Murray, 2015), we also expect laypeople to intuitively follow the logic of the **wisdom of crowds**: the ability of an **aggregate of estimates** (rather than a single estimate) to **reduce noise** stemming from individual bias or error (Schweinsberg et al., 2021).  
  $~~~~~$ In contrast, when crowd estimates show low consensus and high variance (the **inconsistent crowd** condition), we predict that observers will be less swayed and more likely to **attribute** the findings to **bias** and **error**. In addition, due to the difficulty of lay reasoning about variation (Ben-Zvi & Garfield, 1999), we predict an **aversion to variability**: i.e., we expect that observing variable estimates will decrease lay **confidence** in the precise average parameter estimate in both crowd conditions.

# Hypotheses
 **Table 1**: *Predicted differences with the single estimate condition*

| Measure | Consistent crowd | Inconsistent crowd |
| ------------- |  ------------- | ------------- | 
| 1. Posterior beliefs in the phenomenon | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`  | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` |
|2. Credibility of the results | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` |
| 3. Confidence in the precise estimate  | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`  | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | 
| 4. Bias | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` |
| 5. Error | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | $~~~~~~~~~~$ `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` |
| 6. Discretion | $~~~$ No prediction | $~~~$ No prediction |  
*Note.* We regress each outcome on **prior beliefs** and **condition** (with the **single estimate condition** as the **reference category**). When laypeople observe multiple consistent (inconsistent) estimates from a crowd, we expect -- compared to a single estimate and controlling for prior beliefs -- higher (lower) **posterior beliefs** and **credibility** of the results, lower **confidence** in the precise average parameter estimate, and lower (higher) ratings of **bias** and **error**.

**Open Science:** Preregistration, survey, data, and code available at        
`r icon_style(icons::fontawesome("github"), scale = 1.3, fill = "#035AA6")` $~~$ [Insert GitHub link here]   
`r icon_style(icons::academicons("osf"), scale = 1.3, fill = "#035AA6")` $~~$ [Insert OSF link here]

@@

We ran an experiment (*N* = 1,498; UK/US Prolific) with **three conditions**  
`r icon_style(icons::fontawesome("dice-one"), scale = 1.5, fill = "#035AA6")` $~$ **Single estimate**  
A single parameter estimate (5%)   
`r icon_style(icons::fontawesome("dice-two"), scale = 1.5, fill = "#035AA6")` $~$ **Consistent crowd**  
Multiple crowd estimates: low variance, high consensus (M = 5%)  
`r icon_style(icons::fontawesome("dice-three"), scale = 1.5, fill = "#035AA6")` $~$ **Inconsistent crowd**  
Multiple crowd estimates: high variance, low consensus (M = 5%)

@@

**Figure 1**: *Estimates of differences with the single estimate condition*
```{r, echo = FALSE, out.width='93%', fig.retina=3, fig.align='left'}
knitr::include_graphics("Figure1.jpg")
```
**In line with our hypotheses**, lay consumers of **inconsistent crowd estimates** (vs. a single estimate)...  
`r icon_style(icons::fontawesome("arrow-circle-down"), scale = 1.5, fill = "red")` $~~$ Have lower posterior beliefs about the reported phenomenon  
`r icon_style(icons::fontawesome("arrow-circle-down"), scale = 1.5, fill = "red")` $~~$ Find the results less credible  
`r icon_style(icons::fontawesome("arrow-circle-down"), scale = 1.5, fill = "red")` $~~$ Have less confidence in the average estimate of 5%  
`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~$ Are more likely to attribute the average estimate (5%) to bias   
`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~$ Are more likely to attribute the average estimate (5%) to error

**Contrary to our hypotheses**, lay consumers of **consistent crowd estimates** (vs. a single estimate)...  
`r icon_style(icons::fontawesome("arrow-circle-down"), scale = 1.5, fill = "red")` $~~$ Have lower posterior beliefs about the reported phenomenon  
`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~$ Are more likely to attribute the average estimate (5%) to error

We found **no significant effects** for lay consumers of **consistent crowd estimates** (vs. a single estimate) on...  
`r icon_style(icons::fontawesome("question-circle"), scale = 1.5, fill = "grey")` $~~$ Credibility of the results  
`r icon_style(icons::fontawesome("question-circle"), scale = 1.5, fill = "grey")` $~~$ Confidence in the average estimate   
`r icon_style(icons::fontawesome("question-circle"), scale = 1.5, fill = "grey")` $~~$ Ratings of bias

@@

For the additional **exploratory measure**, lay consumers of consistent and inconsistent **crowd estimates**...  
`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~$ Perceive greater discretion (i.e., idiosyncratic choices)

**Figure 2**: *Distribution of prior and posterior beliefs by condition*  
```{r, echo = FALSE, out.width='100%', fig.retina=3, fig.align='center'}
knitr::include_graphics("Figure2b.jpg")
```

In terms of **belief updating**, Figure 2 shows a positive difference within the consistent crowd condition $($pre vs. post $M_d$ = 4.75 [2.55,6.95]$)$, but less so than for the single estimate condition $(M_d$ = 11.66 [9.66,13.66]$)$. As expected, we find negative belief updating in the inconsistent crowd condition $(M_d$ = -11.45 [-13.75,-9.16]$)$.

# Conclusion 
 $~~$ **Compared to providing a single estimate, we find no evidence that**   
 $~~~~~~~$ **crowd estimates improve lay perceptions of scientific findings**

**Future Directions**  
`r icon_style(icons::fontawesome("question-circle"), scale = 1.5, fill = "#035AA6")` $~~$ Does **variability aversion** explain the findings?  
`r icon_style(icons::fontawesome("flask"), scale = 1.5, fill = "#035AA6")` $~~~$ Perceptions of **scientists**  
`r icon_style(icons::fontawesome("comments"), scale = 1.5, fill = "#035AA6")` $~~$ **Science communication** and **communicating uncertainty**
